Types for R, Empirically Designed and Evaluated

### 2020-05-07 paper/main.tex
initial list discussion

@@

>>>>

\AT{I'll revisit this section to adjust for the final details, as the analysis has changed since this was written.}

@@

\AT{List rehash.}
Separate from the vectorized primitives in R are lists:
Whereas vectors are homogeneous and restricted to primitive types, lists can contain arbitrarily-typed data.
R even builds on lists to create a more complex data structure known as the {\it data frame}, an essential data structure to R's functionality \AT{maybe too aggressively worded, but we can back this up with data, e.g. how many functions take data frames?}.

\AT{Outline concerns for typing.}
We are faced with several possible designs for list types.
Chief concerns include the heterogeneity of list elements, and the presence of a \code{names} attribute, allowing list elements to be accessed in a struct-like manner.
\AT{Rarely?}, programmers even write code expecting lists of a particular pre-defined length.
The next sections highlight some important design decisions for our list types.

\AT{Dig into concerns for typing.}

%
%
\subsubsection{Forgoing Tuples, or Short, Constant Length Lists}

We briefly entertained the possibility of including a \code{tuple} type, which would have looked like e.g. \code{tuple<int, int>} for a list of two integers.
When configured to detect tuples, our analysis did indeed pick up \AT{a number}, but post-processing and simplification revealed that in \AT{many} cases, they would be subsumed by co-occurring \code{list} types.
In other words, it just so happened that functions were being called with short lists.
Of the cases that tuples were not subsumed by lists, \AT{often} there were \AT{tuples of different lengths}, implying that the shape of the argument was not essential.
\AT{Wording...}

%
%
\subsubsection{Forgoing Structs}

%
%
\subsubsection{Forgoing Data Frames}
